### 2022-11-21 ms.rmd
Adding in some rerun false statements

# Subset the data
lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% mutate(spp = species_full)

# Intercept only model. 
model1.1 <- metafor::rma.mv(effect_size ~ type, V = V, 
                            random = list(~1 + type | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                            R = list(species_full = phylo_cor), dfs = "contain", test = "t", data = lnRRQ10_data)
model1.1_rob <- robust(model1.1, cluster = lnRRQ10_data$record_num)
orchaRd::orchard_plot(model1.1, mod = "type", group  = "record_num", data = lnRRQ10_data, xlab = "lnRRQ10")

>>>>

# Subset the data
lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% 
                              mutate(spp = species_full, c_accl_time = acclim_period - mean(acclim_period, na.rm = TRUE))

# Found some other data entry problems from old dataset. Sample sizes are decimals. That's not correct. It has to be an integer. Need to check. These are not the new data that we entered. 
hist(lnRRQ10_data$V)

# Studies with big V, why? Check N
lnRRQ10_data %>% filter(V >= 2)

# Intercept only model. 
rerun = FALSE
if(rerun){
  model1.1 <- metafor::rma.mv(effect_size ~ c_accl_time + type, V = V, 
                              random = list(~1 | record_num,
                                              ~1 | species_full,
                                              ~1 | spp,
                                              ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data) 
  # Save model1.1
  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
} else{ model1.1 <- readRDS("./output/models/lnRRQ10_1.1")}

# Robust variance estimation
model1.1_rob <- robust(model1.1, cluster = lnRRQ10_data$record_num)

# OrchaRd plot of model 1.1
p1.1 <- orchaRd::orchard_plot(model1.1, mod = "type", group  = "record_num", data = lnRRQ10_data, 
                              xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45)

if(rerun){
  # More realistic model with 
  model1.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
                              random = list(~1 + type | record_num,
                                              ~1 | species_full,
                                              ~1 | spp,
                                              ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

  # Save model1.2
  saveRDS(model1.2, file = "./output/models/lnRRQ10_1.2")
} else{
  model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
}

# Robust variance
model1.2_rob <- robust(model1.2, cluster = lnRRQ10_data$record_num)

# Orchard plot
p1.2 <- orchaRd::orchard_plot(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data, xlab = TeX("$lnRR_{Q_{10}}$"), angle = 45, legend.pos = "top.left") + scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) +
  theme(legend.direction = "vertical") + 
  geom_segment(aes(x = 2.92, y = 2, xend = 3.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
                geom_segment(aes(x = 1.92, y = 2, xend = 2.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
               geom_segment(aes(x = 0.92, y = 2, xend = 1.07, yend = 2), 
                            arrow = arrow(angle = 90, ends = "both", length = unit(0.01, "npc"))) +
                   annotate("text", x = 1, y = 2.50, 
                            label =TeX(paste0("$\\beta = $", round(model1.2$b[3], 2), " [", round(model1.2$ci.lb[3], 2)," - ", round(model1.2$ci.ub[3], 2), "] ", round((model1.2$b[3] / model1.2$b[1]*100), 2), "%")), hjust = 0)
